### 2017-03-24 manuscript.rmd
started ti implement density difference plots

```{r preliminaries, echo=FALSE, message=F, warning=F}
	library( treeio )
	library( tidyverse )
	library( magrittr )
	library( stringr )
	library( parallel )
	library( ggtree )
	library( ape )
	library( digest )
	library( hutan ) # From https://github.com/caseywdunn/hutan
	library( gridExtra )
	library( geiger )
	library( phytools )

>>>>

```{r preliminaries, echo=FALSE, message=F, warning=F}
	library( treeio ) # https://bioconductor.org/packages/devel/bioc/html/treeio.html
	library( ggtree ) # https://bioconductor.org/packages/release/bioc/html/ggtree.html
	library( hutan ) # https://github.com/caseywdunn/hutan

	# The rest can be installed from CRAN
	library( tidyverse )
	library( magrittr )
	library( stringr )
	library( parallel )
	library( ape )
	library( digest )
	library( gridExtra )
	library( geiger )
	library( phytools )
